Workflow

### 2015-06-15 Workflow/Workflow.Rmd
Added a section on dowloading to Matt's laptop.
Additional text on resampline results.

>>>>

### 
* If Randy has run the analysis, resampling results can be placed in `/home/rpruim/Share`. 
* To download resampling results to his laptop, Matt can say, for example, `scp -P 22122 mkh2@dahl.calvin.edu:/home/rpruim/Share/2015-06-11-run/data_resample/Calvin/* ~/github/Econ-Growth-R-Analysis/data_resample/Calvin`
